Flabby and injective objects in toposes

### 2022-02-13 paper-flabby-objects.tex
Remark on a potential variant of the definition

Since we want to develop an analogous theory for flabby objects in elementary
toposes, it is worthwhile to analyze the logical and set-theoretic commitments
which are required to establish these properties. The standard proofs of
properties~(1),~(3a),~(3b) and~(3c) require Zorn's lemma to construct maximal
extensions of given sections.\footnote{We are careful to distinguish between
the axiom of choice and Zorn's lemma. The former implies the latter, but the
converse requires the law of excluded middle.}
The standard proof of property~(4b) requires the
law of excluded middle, to ensure that the Godement construction actually
yields a flabby sheaf. Properties~(2) and~(4a) can be verified purely
intuitionistically.

@@

\begin{defn}\label{defn:flabby-sheaf}
A sheaf~$F$ on a topological space (or locale)~$X$ is \emph{flabby}
if and only if for all opens~$U$ and all sections~$s \in F(U)$, there is an
open covering~$X = \bigcup_i U_i$ such that, for all~$i$, the section~$s$ can
be extended to a section on~$U \cup U_i$.\end{defn}
\XXX{choice-free formulation}

>>>>

Since we want to develop an analogous theory for flabby objects in elementary
toposes, it is worthwhile to analyze the logical and set-theoretic commitments
which are required to establish these properties. The standard proofs of
properties~(1),~(3a),~(3b) and~(3c) require Zorn's lemma to construct maximal
extensions of given sections.\footnote{We are careful to distinguish between
the axiom of choice and Zorn's lemma. The former implies the latter, but the
converse implication requires the law of excluded middle.}
The standard proof of property~(4b) requires the
law of excluded middle, to ensure that the Godement construction actually
yields a flabby sheaf. Properties~(2) and~(4a) can be verified purely
intuitionistically.

@@

\begin{defn}\label{defn:flabby-sheaf}
A sheaf~$F$ on a topological space (or locale)~$X$ is \emph{flabby}
if and only if for all opens~$U$ and all sections~$s \in F(U)$, there is an
open covering~$X = \bigcup_i U_i$ such that, for all~$i$, the section~$s$ can
be extended to a section on~$U \cup U_i$.\footnote{Even in the absence of the
axiom of choice it doesn't make a difference
whether we are stipulating, as in the definition, for each index~$i \in I$ the mere
existence of an extension~$t \in F(U \cup U_i)$, or whether we are stipulating
the existence of a family~$(t_i)_i$ of extensions~$t_i \in F(U \cup U_i)$.
Clearly, the existence of the family implies the existence of individual
extensions. Conversely, if for each~$i \in I$ there exists an extension, there
is a tautologous family of extensions over the enlarged index set~$I' \defeq \{
(i,t) \,|\, i \in I, t \in F(U \cup U_i), t|_U = s \}$, and we still have~$X =
\bigcup_{(i,t) \in I'} U_i$.}
\end{defn}
